Modeling How Evolution in One Trait is Affected by Adaptation in Another

### 2017-10-01 manuscript.tex
more simulations started and fixed data collection to speed up simulations.

\begin{subfigure}[b]{0.48\linewidth}
\centering
\includegraphics[width=1\linewidth]{fig5f.pdf}
\caption{}\label{fig:2c}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
\centering
\includegraphics[width=1\linewidth]{fig5g.pdf}
\caption{}\label{fig:2d}
\end{subfigure}
\caption{\footnotesize 
(a-c) Magnitudes of the mean variance, covariance, and rate of adaptation for trait one divided by its expected rate of adaptation when evolving without a second. Each plot includes the measured values produced by simulations with either varying $s$, $U$, or $N$. (d) Expected decrease in the rate of adapatation of trait, when additional traits are added for three choices of $s$. Changes in the scaled mean variances and covarainces vary only slightly with changes in each of three parameters. The decrease in a trait's rate of adaptation is nearly 60\% across changes in each of the three parameters. Fixed simulation parameters in (a-c) are: $s=10^{-2}$, $U=10^{-5}$ and $N=10^9$.}\label{fig:2}
\end{figure}
% *****************************************************************************************************************
% ***********************************END*FIGURE*2******************************************************************
% *****************************************************************************************************************

>>>>

\begin{subfigure}[b]{0.48\linewidth}
\centering
\includegraphics[width=1\linewidth]{fig5f.pdf}
\caption{}\label{fig:2c}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
\centering
\includegraphics[width=1\linewidth]{fig5g.pdf}
\caption{}\label{fig:2d}
\end{subfigure}
\caption{\footnotesize 
(a-c) Magnitudes of changes in mean variance, covariance, and rate of adaptation of trait one divided by its expected rate of adaptation when evolving without the second. Each plot includes the measured values produced by simulations with either varying $s$, $U$, or $N$. (d) The expected decrease in trait one's rate of adapatation for various numbers of traits added.  Three choices of $s$ are shown to depict its effect. Adaptation in a single trait is affected in two ways when evolving with a second trait. First, its variance increases due to classes with poorer backgrounds in the first trait persisting longer when they are fit in the second. In (a-c), the increase (dashed line) ranges from 60\% to 100\% depending on the parameter.  The second effect, involves the formation of negative covariance between the two traits. Its magnitude (dotted line) is substantially larger, ranging from 80\% to 140\%, and always 40\% larger than the increase in variance. This results in a net decrease of 40\% in the rate of adaptation (solid line). Fixed simulation parameters in (a-c) are: $s=10^{-2}$, $U=10^{-5}$ and $N=10^9$.}\label{fig:2}
\end{figure}
% *****************************************************************************************************************
% ***********************************END*FIGURE*2******************************************************************
% *****************************************************************************************************************
